Output Summary

### 2023-05-02 03-post-process/output-plots-children/03-fit-to-data.Rmd
Consistency updates: 03-fit-to-data.Rmd

```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Pa[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
               yrs = all_yrs[ts_yrs],
               main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Fall Parr Abundance")
```

@@

```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Mb[year,LH_type,origin,pop]$", year = ts_yrs, origin = o_nor, LH_type = i_spring, pop = j)), 
               get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Spring Smolt Abundance")
```

@@

```{r adult-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Ra_tot[year,pop]$", year = ts_yrs, pop = j)),
               get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Adult Return Abundance")
```

@@

```{r summer-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[year,pop]", year = ts_yrs, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow LGR\\,Survival$"))
```

@@

```{r fall-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Fall\\,Parr \\rightarrow LGR\\,Survival$"))
```

@@

```{r winter-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_spring, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Winter\\,Parr \\rightarrow LGR\\,Survival$"))
```

@@

```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_nor, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
               main = pops[j], yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(NOR)$"))
```

@@

```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
               main = pops[j], yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(HOR)"))
```

#### LGR Smolt $\rightarrow O_0$ (NOR)

```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_nor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

#### LGR Smolt $\rightarrow O_0$ (HOR)

```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_hor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

#### BON Adults $\rightarrow$ LGR (NOR)

```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_nor], jags_data$x_BON[observable,o_nor] - jags_data$x_LGR[observable,o_nor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

#### BON Adults $\rightarrow$ LGR (HOR)

```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_hor], jags_data$x_BON[observable,o_hor] - jags_data$x_LGR[observable,o_hor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r weir-comp-fit-funcs}

# for multinomial sample size
weir_sample_size = function(j) {
  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
  mp = barplot(jags_data$nx_Ra[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
               ylim = c(0, max(jags_data$nx_Ra[observable,j], na.rm = TRUE)),
               xlab = "Return Year", ylab = "Adults at Weir Sampled for Composition")
  usr = par("usr")
  at_x = seq(1, length(observable), 4)
  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Ra[observable,j]), 3, 4)[at_x])
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
}

@@

  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^p_Ra[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])

  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each age, aggregated across origins
weir_comp_fit_plot_age = function(j) {
  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each origin, aggregated across ages
weir_comp_fit_plot_origin = function(j) {
  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))

  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}
```

@@

```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(j_cat)
```

@@

```{r los-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(j_los)
```

@@

```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(j_min)
```

@@

```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(j_ugr)
```

@@

```{r cat-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
weir_comp_fit_plot_age(j_cat)
```

@@

```{r los-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
weir_comp_fit_plot_age(j_los)
```

@@

```{r min-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
weir_comp_fit_plot_age(j_min)
```

@@

```{r ugr-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
weir_comp_fit_plot_age(j_ugr)
```

@@

```{r cat-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_origin(j_cat)
```

@@

```{r los-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_origin(j_los)
```

@@

```{r min-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_origin(j_min)
```

@@

```{r ugr-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_origin(j_ugr)
```

@@

```{r cat-weir-ss, fig.width = 6, fig.height = 4}
weir_sample_size(j_cat)
```

@@

```{r los-weir-ss, fig.width = 6, fig.height = 4}
weir_sample_size(j_los)
```

@@

```{r min-weir-ss, fig.width = 6, fig.height = 4}
weir_sample_size(j_min)
```

@@

```{r ugr-weir-ss, fig.width = 6, fig.height = 4}
weir_sample_size(j_ugr)
```

@@

```{r carc-comp-fit-funcs}

# for multinomial sample size
carc_sample_size = function(j) {
  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
  mp = barplot(jags_data$nx_Sa_prime[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
               ylim = c(0, max(jags_data$nx_Sa_prime[observable,j], na.rm = TRUE)),
               xlab = "Return Year", ylab = "Carcasses Sampled for Composition")
  usr = par("usr")
  at_x = seq(1, length(observable), 4)
  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Sa_prime[observable,j]), 3, 4)[at_x])
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
}

@@

```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(j_cat)
```

@@

```{r los-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(j_los)
```

@@

```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(j_min)
```

@@

```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(j_ugr)
```

@@

```{r cat-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
carc_comp_fit_plot_age(j_cat)
```

@@

```{r los-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
carc_comp_fit_plot_age(j_los)
```

@@

```{r min-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
carc_comp_fit_plot_age(j_min)
```

@@

```{r ugr-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
carc_comp_fit_plot_age(j_ugr)
```

@@

```{r cat-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_origin(j_cat)
```

@@

```{r los-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_origin(j_los)
```

@@

```{r min-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_origin(j_min)
```

@@

```{r ugr-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_origin(j_ugr)
```

@@

```{r cat-carc-ss, fig.width = 6, fig.height = 4}
carc_sample_size(j_cat)
```

>>>>

```{r fall-trap-N-fit, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^Pa[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               obs = get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
               yrs = all_yrs[ts_yrs], label_text = pops[j], y_scale = 1000, pt_cex = pt_cex)
}

# loop over populations
mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Fall Parr Abundance (1000s)")
```

@@

```{r spring-trap-N-fit, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^Mb[year,LH_type,origin,pop]$", year = ts_yrs, origin = o_nor, LH_type = i_spring, pop = j)), 
               obs = get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
               yrs = all_yrs[ts_yrs], label_text = pops[j], y_scale = 1000, pt_cex = pt_cex)
}

# loop over populations
mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Spring Smolt Abundance (1000s)")
```

@@

```{r adult-N-fit, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^Ra_tot[year,pop]$", year = ts_yrs, pop = j)),
               obs = get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
               yrs = all_yrs[ts_yrs], label_text = pops[j], y_scale = 1000, pt_cex = pt_cex)

# loop over populations
mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Return Year", "Adult Return Abundance (1000s)")
```

@@

```{r summer-surv-fit, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^phi_Pb_Ma[year,pop]", year = ts_yrs, pop = j)),
               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
}

# loop over populations
mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Summer Parr \u2192 LGR Survival")
```

@@

```{r fall-surv-fit, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
}

# loop over populations
mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Fall Parr \u2192 LGR Survival")
```

@@

```{r winter-surv-fit, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_spring, pop = j)),
               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
}

# loop over populations
mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Winter Parr \u2192 LGR Survival")
```

@@

```{r spring-surv-fit-nor, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_nor, pop = j)),
               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
}

# loop over populations
mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Spring Smolt \u2192 LGR Survival (NOR)")
```

@@

```{r spring-surv-fit-hor, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
}

# loop over populations
mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Spring Smolt \u2192 LGR Survival (HOR)")
```

#### LGR Smolt $\rightarrow$ BON

```{r hydro-down-surv-fit, fig.width = p2_width, fig.height = p2_height}
# function to create the plot for one origin type
plot_f = function(o) {
  plot_tseries(est = post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o)),
               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o], jags_data$sig_Lphi_obs_Ma_O0[observable,o]),
               label_text = c("NOR", "HOR")[o], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
}

# loop over origins
mypar(mfrow = c(1,2))
junk = sapply(1:jags_data$no, plot_f)
axis_labels("Brood Year", "LGR Smolt \u2192 BON")
```

#### BON Adults $\rightarrow$ LGR

```{r hydro-up-nor-surv-fit, fig.width = p2_width, fig.height = p2_height}
# function to create the plot for one origin type
plot_f = function(o) {
  plot_tseries(est = post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o)),
               obs = get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o], jags_data$x_BON[observable,o] - jags_data$x_LGR[observable,o]), 1),
               label_text = c("NOR", "HOR")[o], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
}

# loop over origins
mypar(mfrow = c(1,2))
junk = sapply(1:jags_data$no, plot_f)
axis_labels("Brood Year", "BON \u2192 LGR Survival")
```

@@

```{r weir-comp-fit-funcs}
# for multinomial sample size
weir_sample_size = function(j) {
  mypar(mfrow = c(1,1))
  mp = barplot(jags_data$nx_Ra[observable,j], xaxt = "n", col = tran_cols["data"], border = main_cols["data"],
               ylim = make_lim(0, jags_data$nx_Ra[observable,j]),
               xlab = "", ylab = "")
  usr = par("usr")
  at_x = seq(1, length(observable), 4)
  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Ra[observable,j]), 3, 4)[at_x])
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
  axis_labels("Return Year", "Weir Sample Size")
}

@@

  base_param = sub_index("^p_Ra[year,DIM,pop]$", pop = j, year = ts_yrs)
  labels = paste0("Age-", rep(jags_data$kmin:jags_data$kmax, jags_data$no), " (", rep(c("NOR", "HOR"), each = jags_data$nk), ")")

  # function to draw the time series for one panel: one population/age/origin combo
  plot_f = function(ko) {
    plot_tseries(est = post_summ(post, stringr::str_replace(base_param, "DIM", as.character(ko))),
                 obs = get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], ko),
                 label_text = labels[ko], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
  }

  mypar(mfrow = c(2,3))
  junk = sapply(1:jags_data$nko, plot_f)
  axis_labels("Return Year", "Proportion of Return")
}

# for fits to each age, aggregated across origins
weir_comp_fit_plot_age = function(j) {

  base_param = sub_index("^p_Ra_age[year,DIM,pop]$", pop = j, year = ts_yrs)
  labels = paste0("Age-", jags_data$kmin:jags_data$kmax)

  # function to draw the time series for one panel: one population/age combo
  plot_f = function(k) {
    plot_tseries(est = post_summ(post, stringr::str_replace(base_param, "DIM", as.character(k))),
                 obs = get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], k),
                 label_text = labels[k], yrs = all_yrs[ts_yrs], pt_cex = pt_cex, ylim = ylim_01)
  }

  mypar(mfrow = c(1,3))
  junk = sapply(1:jags_data$nk, plot_f)
  axis_labels("Return Year", "Proportion of Return")
}

# for fits to each origin, aggregated across ages
weir_comp_fit_plot_origin = function(j) {

  base_param = sub_index("^p_Ra_origin[year,DIM,pop]$", pop = j, year = ts_yrs)
  labels = c("NOR", "HOR")

  # function to draw the time series for one panel: one population/origin combo
  plot_f = function(o) {
    plot_tseries(est = post_summ(post, stringr::str_replace(base_param, "DIM", as.character(o))),
                 obs = get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], o),
                 label_text = labels[o], yrs = all_yrs[ts_yrs], pt_cex = pt_cex, ylim = ylim_01)
  }

  mypar(mfrow = c(1,2))
  junk = sapply(1:jags_data$no, plot_f)
  axis_labels("Return Year", "Proportion of Return")
}
```

@@

```{r cat-weir-comp-fit, fig.width = p6_width, fig.height = p6_height}
weir_comp_fit_plot(j_cat)
```

@@

```{r los-weir-comp-fit, fig.width = p6_width, fig.height = p6_height}
weir_comp_fit_plot(j_los)
```

@@

```{r min-weir-comp-fit, fig.width = p6_width, fig.height = p6_height}
weir_comp_fit_plot(j_min)
```

@@

```{r ugr-weir-comp-fit, fig.width = p6_width, fig.height = p6_height}
weir_comp_fit_plot(j_ugr)
```

@@

```{r cat-weir-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
weir_comp_fit_plot_age(j_cat)
```

@@

```{r los-weir-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
weir_comp_fit_plot_age(j_los)
```

@@

```{r min-weir-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
weir_comp_fit_plot_age(j_min)
```

@@

```{r ugr-weir-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
weir_comp_fit_plot_age(j_ugr)
```

@@

```{r cat-weir-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
weir_comp_fit_plot_origin(j_cat)
```

@@

```{r los-weir-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
weir_comp_fit_plot_origin(j_los)
```

@@

```{r min-weir-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
weir_comp_fit_plot_origin(j_min)
```

@@

```{r ugr-weir-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
weir_comp_fit_plot_origin(j_ugr)
```

@@

```{r cat-weir-ss, fig.width = 5, fig.height = 2.5}
weir_sample_size(j_cat)
```

@@

```{r los-weir-ss, fig.width = 5, fig.height = 2.5}
weir_sample_size(j_los)
```

@@

```{r min-weir-ss, fig.width = 5, fig.height = 2.5}
weir_sample_size(j_min)
```

@@

```{r ugr-weir-ss, fig.width = 5, fig.height = 2.5}
weir_sample_size(j_ugr)
```

@@

```{r carc-comp-fit-funcs}
# for multinomial sample size
carc_sample_size = function(j) {
  mypar(mfrow = c(1,1))
  mp = barplot(jags_data$nx_Sa_prime[observable,j], xaxt = "n", col = tran_cols["data"], border = main_cols["data"],
               ylim = make_lim(0, max(jags_data$nx_Sa_prime[observable,j])),
               xlab = "", ylab = "")
  usr = par("usr")
  at_x = seq(1, length(observable), 4)
  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Sa_prime[observable,j]), 3, 4)[at_x])
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
  axis_labels("Return Year", "Carcass Sample Size")
}

@@

```{r cat-carc-comp-fit, fig.width = p6_width, fig.height = p6_height}
carc_comp_fit_plot(j_cat)
```

@@

```{r los-carc-comp-fit, fig.width = p6_width, fig.height = p6_height}
carc_comp_fit_plot(j_los)
```

@@

```{r min-carc-comp-fit, fig.width = p6_width, fig.height = p6_height}
carc_comp_fit_plot(j_min)
```

@@

```{r ugr-carc-comp-fit, fig.width = p6_width, fig.height = p6_height}
carc_comp_fit_plot(j_ugr)
```

@@

```{r cat-carc-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
carc_comp_fit_plot_age(j_cat)
```

@@

```{r los-carc-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
carc_comp_fit_plot_age(j_los)
```

@@

```{r min-carc-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
carc_comp_fit_plot_age(j_min)
```

@@

```{r ugr-carc-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
carc_comp_fit_plot_age(j_ugr)
```

@@

```{r cat-carc-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
carc_comp_fit_plot_origin(j_cat)
```

@@

```{r los-carc-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
carc_comp_fit_plot_origin(j_los)
```

@@

```{r min-carc-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
carc_comp_fit_plot_origin(j_min)
```

@@

```{r ugr-carc-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
carc_comp_fit_plot_origin(j_ugr)
```

@@

```{r cat-carc-ss, fig.width = 5, fig.height = 2.5}
carc_sample_size(j_cat)
```
